Supporting information for ``How environmental drivers of spatial synchrony interact''

### 2022-12-15 Paper/SupMat.Rnw
edits to paper
continued editing to the paper

@@

% \section{Detailed breakdown of terms in the general theory for the case studies}\label{sect:breakdown_case_studies}
% 
% We here provide a detailed technical breakdown how the terms in our main theoretical equation, 
% (\ref{MT-rhoww_T1to3}), capture the complexities of CaseA described in the main text.
% The size of the $1$q lag of the effects of 
% 
% 
% Theory captures these complexities because
% the size of the $1$q lag of this scenario, relative to a timescale, $\sigma$, is captured by
% the phase of $f_{\mcP^{(1)}} \conj{f_{\mcP^{(2)}}} \rho_{\epsilon^{(1)} \epsilon^{(2)}}$, which equals the phase of
% $f_{\mcP^{(1)}} \conj{f_{\mcP^{(2)}}}$ because $l_n=0$ and $\rho_{\epsilon^{(1)} \epsilon^{(2)}}$ is a real number
% (SI section \ref{SM-sect:examples_cross_sync}). But $f_{\mcP^{(1)}} \conj{f_{\mcP^{(2)}}}=
% p_1^{(1)} p_0^{(2)} \mu = p_1^{(1)} p_0^{(2)} \exp(-2 \pi \iota f) =
% p_1^{(1)} p_0^{(2)} \exp(-2 \pi \iota /\sigma)$ (SI section \ref{SM-sect:details_case_studies}),
% which has phase $-\pi$ at short timescales
% and phase almost $0$ at long timescales (Fig. \ref{fig:TheoryCaseA}b,c).
% The phase controls the sign of $2\Rp(f_{\mcP^{(1)}} \conj{f_{\mcP^{(2)}}} \rho_{\epsilon^{(1)} \epsilon^{(2)}})$, the
% interaction term in (\ref{rhoww_T1to3}), as described in General Theory.
% 
% 
% \section{Detailed breakdown of terms in the general theory for kelp}\label{sect:breakdown_kelp}

>>>>

\section{Mathematical details of the example in the Introduction}\label{Sect:IntroExample}
In the case of two environmental variables,
the Moran theorem implies that population synchrony is 
\begin{align}
\cor(w_1,w_2) &= \cor(\epsilon_1^{(1)}+\epsilon_1^{(2)},\epsilon_2^{(1)}+\epsilon_2^{(2)}) \\
&= \frac{\cov(\epsilon_1^{(1)},\epsilon_2^{(1)})+\cov(\epsilon_1^{(1)},\epsilon_2^{(2)})+
\cov(\epsilon_1^{(2)},\epsilon_2^{(1)})+\cov(\epsilon_1^{(2)},\epsilon_2^{(2)})}{
\sqrt{2+2\cov(\epsilon_1^{(1)},\epsilon_1^{(2)})}\sqrt{2+2\cov(\epsilon_2^{(1)},\epsilon_2^{(2)})}}, \\
\end{align}
which depends not only on the 
standard environmental synchrony 
measures $\cov(\epsilon_1^{(a)},\epsilon_2^{(a)})$, for 
$a=1,2$, but also on the ``cross synchrony'' measures $\cov(\epsilon_1^{(a)},\epsilon_2^{(b)})$
for $a \neq b$.

@@
